HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-15 paper/main.tex
misc
sss

\author{
  Alexandra Birch\textsuperscript{1}, Omri Abend\textsuperscript{2}, Ond{\v{r}}ej Bojar\textsuperscript{3},
  Barry Haddow\textsuperscript{1*}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\textsuperscript{3} Charles University in Prague, Faculty of Mathematics and Physics\\
\texttt{a.birch@ed.ac.uk, oabend@cs.huji.ac.il}\\
\texttt{bojar@ufal.mff.cuni.cz, bhaddow@inf.ed.ac.uk}\\
}

@@

\let\thefootnote\relax\footnotetext{*All authors contributed equally to this work.}

@@

In other cases, HMEANT's does not to penalize errors. For instance, as HMEANT is defined as an aggregate
of the scores given to the slot fillers, it cannot assign partial scores to the predicates themselves in
cases of a divergent tense or a negation flip. Consider the following:

@@

The translation is mostly understandable, although the verb ``{\"u}berspringen'' is incorrectly inflected.
HUME allows marking it as Orange (as it was  indeed annotated in our experiments), while
HMEANT allows either to mark it as correct, or otherwise mark the entire frame as a ``no match''.

>>>>

\author{
  Alexandra Birch\textsuperscript{1}\thanks{$^*$ All authors contributed equally to this work.} , Omri Abend\textsuperscript{2*}, Ond{\v{r}}ej Bojar\textsuperscript{3*},
  Barry Haddow\textsuperscript{1*}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\textsuperscript{3} Charles University in Prague, Faculty of Mathematics and Physics\\
\texttt{a.birch@ed.ac.uk, oabend@cs.huji.ac.il}\\
\texttt{bojar@ufal.mff.cuni.cz, bhaddow@inf.ed.ac.uk}\\
}

@@

%\let\thefootnote\relax\footnotetext{*All authors contributed equally to this work.}

@@

\com{
In other cases, HMEANT's does not to penalize errors. For instance, as HMEANT is defined as an aggregate
of the scores given to the slot fillers, it cannot assign partial scores to the predicates themselves in
cases of a divergent tense or a negation flip. Consider the following:

@@

The translation is mostly understandable, although the verb ``{\"u}berspringen'' is incorrectly inflected.
HUME allows marking it as Orange (as it was  indeed annotated in our experiments), while
HMEANT allows either to mark it as correct, or otherwise mark the entire frame as a ``no match''.
}
